Thesis: draft

### 2021-04-16 draft.tex
latest update

\newpage
\noindent
\textbf{Making a fraction of the nodes completely stubborn}\\
\newline
We start by making a fraction of the nodes (fracRes) completely stubborn ($r_i = 1$). We go from no stubborn nodes, fracRes $=0$, to all the nodes are stubborn, fracRes $=1$. In all cases, the stubborn nodes are randomly distributed over the network.\\

@@

@@

  	\includegraphics[width=8cm, height=7cm]{echo_chamber_vs_stubbornness_frac_compl_stubb_REF_8x7.png}

@@

  	\includegraphics[width=8cm, height=7cm]{echo_chamber_vs_stubbornness_frac_compl_stubb_REC_8x7.png}

@@

    \label{REC_frac_compl_stubb}

@@

  \caption[Formation of echo chambers versus fraction of completely stubborn nodes for the REF and REC filtering algorithms and an initial $50/50$ opinion distribution]{Formation of echo chambers versus the fraction of completely stubborn nodes, fracRes, for an initial $50/50$ opinion distribution. \textbf{(a)} Using the REF filtering algorithm; \textbf{(b)} Using the REC filtering algorithm. The $y$-axis shows the average of the normalized fraction of nodes with all neighbors having opinion 0 and the normalized fraction of nodes with all neighbors having opinion 1. This value represents the formation of echo chambers in the system (denoted with echo chamber size in the figure). Results are shown for four different network models, each with a total number of nodes $N=10^3$ and an average degree around $\left<k\right> \sim 10$: WS network with $K =10,\ \beta = 0.06$ and $\left<C\right> \sim 0.55$; SBM-WS network with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$; SBM network with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; ER network with $p= 0.01$. Each data point is the result of $10^2$ independent simulations.}
\label{echo_vs_frac_complStubb_REF-REC}

@@

We can conclude that the formation of echo chambers versus the fraction of completely stubborn people, for an initial $20/80$ opinion distribution, qualitatively resembles the results for an initial $50/50$ opinion distribution (decrease in formation of echo chambers with an increasing fraction of stubborn agents for the PR method versus an increase in the formation of echo chambers with an increasing fraction of stubborn people, followed by a decrease for the REC method).

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{echo_chamber_vs_frac_compl_stubb_PR_20-80_8x7.png}
    \caption{PR}
    \label{PR_frac_compl_stubb_20-80}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{echo_chamber_vs_frac_compl_stubb_REC_20-80_8x7.png}
    \caption{REC}
    \label{REC_frac_compl_stubb_20-80}
  \end{subfigure}
  \captionsetup{format=plain}
  \caption[Formation of echo chambers versus fraction of completely stubborn nodes for the PR and REC filtering algorithms and an initial $20/80$ opinion distribution]{Formation of echo chambers versus the fraction of completely stubborn nodes, fracRes, for an initial $20/80$ opinion distribution. \textbf{(a)} Using the PR filtering algorithm; \textbf{(b)} Using the REC filtering algorithm. The $y$-axis shows the total number of like-minded neighborhoods (sum of the number of echo chambers around opinion 0 and the number of echo chambers around opinion 1) at $t=500$ divided by the total number of like-minded neighborhoods at $t=0$. This value represents the formation of echo chambers in the system (denoted with echo chamber size in the figure). Results are shown for four different network models, each with a total number of nodes $N=10^3$ and an average degree around $\left<k\right> \sim 10$: WS network with $K =10,\ \beta = 0.06$ and $\left<C\right> \sim 0.55$; SBM-WS network with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$; SBM network with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; ER network with $p= 0.01$. Each data point is the result of $10^2$ independent simulations.}
\label{echo_vs_frac_complStubb_PR-REC_20-80}
\end{figure}

% don't forget the evolution of opinions + also for 20/80, do each network, PR, REC, REF for eg. stubb 0.4 (so two fig (50-50 and 20-80) with 4 subplots (one for each network), each plot has PR, REF, REC) + if all stubb frac behaves same, explain in text, if not make extra plot!!
\noindent
\textbf{Making all nodes partly stubborn}\\
\newline
All the nodes are given the same stubbornness parameter $r$ and we let this stubbornness parameter vary from $r = 0$ (all the nodes are completely willing to change opinions) to $r=1$ (all the nodes are completely stubborn).\\
\newline
Figure \ref{echo_vs_all_frac_stubb_PR} shows the formation of echo chambers versus the stubbornness parameter of all the nodes, $r$, for an initial $50/50$ opinion distribution and using the PR filtering algorithm. The interpretation of the $y$-axis is again as explained in Section \ref{echoVSmod} and the data points are shown together with their standard error $SE$. The results look very similar to the case where a fraction of the nodes is completely stubborn and when using the PR method, which is depicted in Figure \ref{echo_vs_frac_complStubb}.\\
The Erd\H{o}s-R\'{e}nyi model has no appearance of echo chambers, as before, and this is not changed by making the nodes more and more stubborn. The same result is obtained for the stochastic block model with a low modularity (the data points lie again behind those of the ER network).\\
The stochastic block model with a high modularity has a (small) formation of echo chambers for $r=0$. If the nodes become more and more convinced of their own opinion ($r$ increases), the formation of echo chambers decreases.\\
This is especially visible for the high clustering networks (WS and SBM-WS), which have the highest formation of echo chambers for $r=0$. If $r$ increases and the nodes become more and more convinced of their own beliefs, which makes them less and less willing to change that belief, the formation of echo chambers starts to decrease. If $r=1$, the nodes retain their initial opinion and the number of echo chambers before and after the time evolution remains the same. In Figure \ref{echo_vs_all_frac_stubb_PR} this is represented by an echo chamber size equal to one for $r=1$.

@@

@@

>>>>

\newpage
\noindent
\textbf{Making a fraction of the nodes completely stubborn}\\
\newline
We start by making a fraction of the nodes (fracRes) completely stubborn ($r_i = 1$). We go from no stubborn nodes, fracRes $=0$, to all the nodes are stubborn, fracRes $=1$. In all cases, the stubborn nodes are randomly distributed over the network.\\
We will first discuss the formation of echo chambers for an initial $50/50$ opinion distribution, after which the results for the opinion evolution will be shared.

@@

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{echo_chamber_vs_stubbornness_frac_compl_stubb_REF_8x7.png}
    \caption{REF}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{echo_chamber_vs_stubbornness_frac_compl_stubb_REC_8x7.png}
    \caption{REC}
    \label{REC_frac_compl_stubb}
  \end{subfigure}
  \captionsetup{format=plain}
  \caption[Formation of echo chambers versus fraction of completely stubborn nodes for the REF and REC filtering algorithms and an initial $50/50$ opinion distribution]{Formation of echo chambers versus the fraction of completely stubborn nodes, fracRes, for an initial $50/50$ opinion distribution. \textbf{(a)} Using the REF filtering algorithm; \textbf{(b)} Using the REC filtering algorithm. The $y$-axis shows the average of the normalized fraction of nodes with all neighbors having opinion 0 and the normalized fraction of nodes with all neighbors having opinion 1. This value represents the formation of echo chambers in the system (denoted with echo chamber size in the figure). Results are shown for four different network models, each with a total number of nodes $N=10^3$ and an average degree around $\left<k\right> \sim 10$: WS network with $K =10,\ \beta = 0.06$ and $\left<C\right> \sim 0.55$; SBM-WS network with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$; SBM network with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; ER network with $p= 0.01$. Each data point is the result of $10^2$ independent simulations.}
\label{echo_vs_frac_complStubb_REF-REC}
\end{figure}
\noindent
So far the results for the formation of echo chambers in the system for an initial $50/50$ opinion distribution and introducing a fraction of completely stubborn agents. But what about the evolution of the opinions over time? Are these affected by introducing stubborn people in the system? \\
\newline
In Figure \ref{ev_op_50_50_stubb_REC} the evolution of the fraction of nodes with opinion 0 for an initial $50/50$ opinion distribution is shown. Data points are shown together with the standard deviation $\sigma$. This figure shows the results for the REC filtering algorithm. The four network models (ER, WS, SBM (high and low modularity) and SBM-WS) are compared to each other. For each model we look at three different fractions of completely stubborn people: no stubborn people, fracRes $=0$; a fraction of completely stubborn people equal to fracRes $=0.4$ and a fraction of completely stubborn people equal to fracRes $=0.8$. Introducing a fraction of stubborn people is not able to break the initial $50/50$ opinion distribution for neither of the network models.\\
\newline
Figure \ref{ev_op_50_50_stubb_PR} shows the results for the evolution of the fraction of opinion 0 in the system for an initial $50/50$ opinion distribution and when using the PR filtering algorithm. Data points are again represented together with the standard deviation $\sigma$. Three different fractions of stubborn people (fracRes $=0$, fracRes $=0.4$ and fracRes $=0.8$) are compared to each other for the four different network models. The results don't differ from those obtained for the REC filtering algorithm. The status-quo is maintained, the initial $50/50$ opinion distribution does not change over time when introducing stubborn people and using the PR filtering algorithm.

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_ER_frac_compl_stubb_REC_8x7.png}
    \caption{ER}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_WS_frac_compl_stubb_REC_8x7.png}
    \caption{WS}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_frac_compl_stubb_REC_8x7.png}
    \caption{SBM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM-WS_frac_compl_stubb_REC_8x7.png}
    \caption{SBM-WS}
  \end{subfigure}
  \captionsetup{format=plain}
  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ opinion distribution, using the REC filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$)]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ distribution, using the REC filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$). Four different network models are used (each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$): \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?
\label{ev_op_50_50_stubb_REC}
\end{figure}

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_ER_frac_compl_stubb_PR_8x7.png}
    \caption{ER}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_WS_frac_compl_stubb_PR_8x7.png}
    \caption{WS}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_frac_compl_stubb_PR_8x7.png}
    \caption{SBM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM-WS_frac_compl_stubb_PR_8x7.png}
    \caption{SBM-WS}
  \end{subfigure}
  \captionsetup{format=plain}
  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ opinion distribution, using the PR filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$)]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ distribution, using the PR filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$). Four different network models are used (each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$): \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?
\label{ev_op_50_50_stubb_PR}
\end{figure}
\noindent
Up till now, we have discussed the results for the formation of echo chambers and the evolution of the opinions when introducing a fraction of completely stubborn nodes in the system for an initial $50/50$ opinion distribution. Lets now look at the results for introducing a fraction of stubborn agents when we are dealing with an unbalanced initial opinion distribution, eg. an initial $20/80$ distribution.\\
\newline

@@

  	\includegraphics[width=8cm, height=7cm]{echo_chamber_vs_frac_compl_stubb_PR_20-80_8x7.png}
    \label{PR_frac_compl_stubb_20-80}

@@

  	\includegraphics[width=8cm, height=7cm]{echo_chamber_vs_frac_compl_stubb_REC_20-80_8x7.png}

@@

    \label{REC_frac_compl_stubb_20-80}

@@

  \caption[Formation of echo chambers versus fraction of completely stubborn nodes for the PR and REC filtering algorithms and an initial $20/80$ opinion distribution]{Formation of echo chambers versus the fraction of completely stubborn nodes, fracRes, for an initial $20/80$ opinion distribution. \textbf{(a)} Using the PR filtering algorithm; \textbf{(b)} Using the REC filtering algorithm. The $y$-axis shows the total number of like-minded neighborhoods (sum of the number of echo chambers around opinion 0 and the number of echo chambers around opinion 1) at $t=500$ divided by the total number of like-minded neighborhoods at $t=0$. This value represents the formation of echo chambers in the system (denoted with echo chamber size in the figure). Results are shown for four different network models, each with a total number of nodes $N=10^3$ and an average degree around $\left<k\right> \sim 10$: WS network with $K =10,\ \beta = 0.06$ and $\left<C\right> \sim 0.55$; SBM-WS network with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$; SBM network with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; ER network with $p= 0.01$. Each data point is the result of $10^2$ independent simulations.}
\label{echo_vs_frac_complStubb_PR-REC_20-80}

@@

We can conclude that the formation of echo chambers versus the fraction of completely stubborn people, for an initial $20/80$ opinion distribution, qualitatively resembles the results for an initial $50/50$ opinion distribution (decrease in formation of echo chambers with an increasing fraction of stubborn agents for the PR method versus an increase in the formation of echo chambers with an increasing fraction of stubborn people, followed by a decrease for the REC method). \\
So much for the formation of echo chambers in case of an unbalanced initial opinion distribution and introducing a fraction of stubborn people in the system. Lets now discuss the evolution of the opinions in the system. In Figure \ref{ev_op_20_80}, we already saw that for a system with no stubborn agents the REC method does not break the prevalence of the initial opinions in case of an initial $20/80$ opinion distribution. The PR filtering algorithm, on the other hand, resulted in a strong decrease of the prevalence of the minority opinion. Are these results affected by introducing stubborn agents?\\
Figure \ref{ev_op_20_80_stubb_REC} shows the evolution of the fraction of nodes with opinion 0 over time for an initial $20/80$ distribution and when using the REC filtering algorithm. Data point are shown together with their standard deviation $\sigma$. Four network models are compared (ER, WS, SBM (high and low modularity) and SBM-WS). For each network model we compare three different fractions of completely stubborn nodes (fracRes $=0$, fracRes $=0.4$ and fracRes $=0.8$). From this figure it becomes clear that introducing stubborn people in combination with the REC filtering algorithm is not able to break the prevalence of the initial opinions in case of an initial $20/80$ opinion distribution. None of the network topologies, nor the stubborn agents can break the status-quo. This result is similar to the case of an initial $50/50$ opinion distribution in combination with a fraction of stubborn people, as discussed for Figure \ref{ev_op_50_50_stubb_REC}.\\
Figure \ref{ev_op_20_80_stubb_PR} shows the results for the fraction of opinion 0 versus time in case of an unbalanced initial opinion distribution and when using the PR filtering algorithm. Data points are presented along with their standard deviation $\sigma$. Again, we compare four different network models (ER, WS, SBM (high and low modularity) and SBM-WS) and for each model we compare the results for three different fractions of stubborn people (fracRes $=0$, fracRes $=0.4$ and fracRes $=0.8$). If there are no stubborn people, the PR leads to a significant decrease in the prevalence of the minority opinion in case of an initial unbalanced opinion distribution. Introducing a fraction of stubborn agents changes this scenario. For an increasing fraction of stubborn people, the decrease of the minority opinion becomes less and less strong. This result is the same for all the different network topologies. If there are no stubborn people, the PR method forces nodes with the minority opinion to switch to the majority opinion. If we however introduce a fraction of stubborn people in the system, then we will also end up with some stubborn nodes that carry the minority opinion. These stubborn nodes with the minority opinion will not switch to the majority opinion, no matter how hard the PR filtering algorithm pushes them. The consequence is that these stubborn people with the minority opinion hamper the decrease of that minority opinion.

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_ER_frac_compl_stubb_REC_20-80_8x7.png}
    \caption{ER}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_WS_frac_compl_stubb_REC_20-80_8x7.png}
    \caption{WS}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_frac_compl_stubb_REC_20-80_8x7.png}
    \caption{SBM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM-WS_frac_compl_stubb_REC_20-80_8x7.png}
    \caption{SBM-WS}
  \end{subfigure}
  \captionsetup{format=plain}
  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $20/80$ opinion distribution, using the REC filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$)]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $20/80$ distribution, using the REC filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$). Four different network models are used (each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$): \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?
\label{ev_op_20_80_stubb_REC}
\end{figure}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_ER_frac_compl_stubb_PR_20-80_8x7.png}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_WS_frac_compl_stubb_PR_20-80_8x7.png}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_frac_compl_stubb_PR_20-80_8x7.png}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM-WS_frac_compl_stubb_PR_20-80_8x7.png}
  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $20/80$ opinion distribution, using the PR filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$)]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $20/80$ distribution, using the PR filtering algorithm and comparing three different fractions of completely stubborn people (fracRes $= 0$, fracRes $= 0.4$ and fracRes $= 0.8$). Four different network models are used (each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$): \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?
\label{ev_op_20_80_stubb_PR}
% don't forget the evolution of opinions + also for 20/80, do each network, PR, REC, REF for eg. stubb 0.4 (so two fig (50-50 and 20-80) with 4 subplots (one for each network), each plot has PR, REF, REC) + if all stubb frac behaves same, explain in text, if not make extra plot!!
\textbf{Making all nodes partly stubborn}\\
Instead of introducing a fraction of completely stubborn people in the system, as was done before, we will now make all the nodes partly stubborn (so they still have some chance of changing their opinion, they are however less eager to do so). All the nodes are given the same stubbornness parameter $r$ and we let this stubbornness parameter vary from $r = 0$ (all the nodes are completely willing to change opinions) to $r=1$ (all the nodes are completely stubborn).\\

@@

Figure \ref{echo_vs_all_frac_stubb_PR} shows the formation of echo chambers versus the stubbornness parameter of all the nodes, $r$, for an initial $50/50$ opinion distribution and using the PR filtering algorithm. The interpretation of the $y$-axis is again as explained in Section \ref{echoVSmod} and the data points are shown together with their standard error $SE$. The results look very similar to the case where a fraction of the nodes is completely stubborn and when using the PR method, which is depicted in Figure \ref{echo_vs_frac_complStubb}.\\
The Erd\H{o}s-R\'{e}nyi model has no appearance of echo chambers, as before, and this is not changed by making the nodes more and more stubborn. The same result is obtained for the stochastic block model with a low modularity (the data points lie again behind those of the ER network).\\
The stochastic block model with a high modularity has a (small) formation of echo chambers for $r=0$. If the nodes become more and more convinced of their own opinion ($r$ increases), the formation of echo chambers decreases.\\
This is especially visible for the high clustering networks (WS and SBM-WS), which have the highest formation of echo chambers for $r=0$. If $r$ increases and the nodes become more and more convinced of their own beliefs, which makes them less and less willing to change that belief, the formation of echo chambers starts to decrease. If $r=1$, the nodes retain their initial opinion and the number of echo chambers before and after the time evolution remains the same. In Figure \ref{echo_vs_all_frac_stubb_PR} this is represented by an echo chamber size equal to one for $r=1$.\\

@@

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_ER_all_frac_stubb_REC_8x7.png}
    \caption{ER}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_WS_all_frac_stubb_REC_8x7.png}
    \caption{WS}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_all_frac_stubb_REC_8x7.png}
    \caption{SBM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM-WS_all_frac_stubb_REC_8x7.png}
    \caption{SBM-WS}
  \end{subfigure}
  \captionsetup{format=plain}
  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ opinion distribution, using the REC filtering algorithm and comparing three different values of the stubbornness parameter $r$ of all the nodes ($r = 0$, $r = 0.4$ and $r = 0.8$)]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ distribution, using the REC filtering algorithm and comparing three different values of the stubbornness parameter $r$ of all the nodes ($r = 0$, $r = 0.4$ and $r = 0.8$). Four different network models are used (each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$): \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?
\label{ev_op_50_50_all_frac_stubb_REC}
\end{figure}

\begin{figure}[H]
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_ER_all_frac__stubb_PR_8x7.png}
    \caption{ER}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
  	\includegraphics[width=8cm, height=7cm]{fraction_of_opinions_WS_all_frac_stubb_PR_8x7.png}
    \caption{WS}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM_all_frac_stubb_PR_8x7.png}
    \caption{SBM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=8cm, height=7cm]{fraction_of_opinions_SBM-WS_all_frac_stubb_PR_8x7.png}
    \caption{SBM-WS}
  \end{subfigure}
  \captionsetup{format=plain}
  \caption[Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ opinion distribution, using the PR filtering algorithm and comparing three different values of the stubbornness parameter $r$ of all the nodes ($r = 0$, $r = 0.4$ and $r = 0.8$)]{Evolution of the fraction of nodes with opinion 0 ($P_0(t)$) over time for an initial $50/50$ distribution, using the PR filtering algorithm and comparing three different values of the stubbornness parameter $r$ of all the nodes ($r = 0$, $r = 0.4$ and $r = 0.8$). Four different network models are used (each with an average degree around $\left<k\right> \sim 10$ and a total number of nodes $N = 10^3$): \textbf{(a)} Erd\H{o}s-R\'{e}nyi model (ER), $p=0.01$; \textbf{(b)} Watts-Strogatz model (WS) with $K = 10$, $\beta = 0.06$ and $\left<C\right> \sim 0.55$; \textbf{(c)} Stochastic block model (SBM) with 10 communities of size 100, a high modularity case ($p_{\text{cl}} = 0.1,\ p_{\text{add}} = 0.001,\ Q \sim 0.9$) and a low modularity case ($p_{\text{cl}} = 0.03,\ p_{\text{add}} = 0.008,\ Q \sim 0.2$) are depicted; \textbf{(d)} Stochastic Watts-Strogatz block model (SBM-WS) with 10 communities of size 100, each community has the following WS parameters: $K = 10,\ \beta = 0.01$ and $p_{\text{add}} = 0.001$, $\left<C\right> \sim 0.55$ and $Q \sim 0.9$. Each plot is the average of $10^2$ independent simulations and data points are shown for every 50 time steps to improve visualization.}%more explanation?
\label{ev_op_50_50_all_frac_stubb_PR}
\end{figure}
